\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-09-03 doc/sw-system.tex
Discussion section plan in place #44

@@

Challenges for future.

@@

>>>>

\todo{Phil}{revisit abstract (\#29).}

@@

\todo{Phil}{write discussion (\#44).}

Preamble. Notes for future. Improvements to system to be investigated.

\subsection{Improving performance: reducing incompleteness and impurity}
\label{sec:discuss:performance}

Incompleteness, false negatives. Examples and trajectories, from stage 2
training set. Generic properties: hard to spot? Or unlucky? Costly mistakes by
expert classifiers? Or random walk?

Impurity, false positives. Examples and trajectories, from stage 2
training set. Generic properties. Could also be solved by dynamical
stage 2? Improve training?

Solutions: dynamical stage 2, to reduce noise. Does stage 1 skill correlate
with stage 2 skill? Missing group-scale lenses at stage 2. Improve training?
Educational interventions?

\subsection{Improving efficiency}
\label{sec:discuss:efficiency}

Inefficiency. Move to truly online system: web app to analyse classifications
as it goes. Place for weekly offline processing? Recovering false negatives by
``resurrecting'' subjects that scattered down too soon.

\subsection{Increasing capacity}
\label{sec:discuss:capacity}

Scaling of system. Factors of ten: 10^4 volunteers, 10^3 achieve high skill,
10^2 make significant contribution. Good project size is few 10^4 subjects, to
enable completion by a crowd of this size in short time.

Ways to increase numbers of high-contribution volunteers: 1) increase crowd
size. Higher exposure through media. Multi-lingual user base - comes with
problems.  2) Increase engagement rate:  feedback from survey teams.

@@

\todo{Phil}{write conclusions (\#45).}
